Project Creditworthiness

### 2021-07-29 Project 3/Assignment/Creditworthiness/Submission - NND.Rmd
Update markdown file

plot.roc(as.numeric(test$Credit_Application_Result),
         as.numeric(y_hat4),
         legacy.axes=TRUE, percent=TRUE,
         xlab="False Positive Percentage",
         ylab="True Postive Percentage",
         print.auc=TRUE,
         print.auc.x=45,
)
legend("bottomright", legend=c("Boosted Tree"))
```
Logistic regresson model has the highest overall accuracy against the Validation set, as well as the highest accuracy within segments. It is also has the most optimal ROC. Therefore, I choose to use logistic regression model.
Applying the chosen model, the number of individuals are creditworthy is 413.
```{r predict}
yhat_final <- predict(model1, validation)
print(sum(yhat_final=='Creditworthy'))
```

>>>>

plot.roc(as.numeric(test$Credit_Application_Result),
         as.numeric(y_hat4),
         legacy.axes=TRUE, percent=TRUE,
         xlab="False Positive Percentage",
         ylab="True Postive Percentage",
         print.auc=TRUE,
         print.auc.x=45,
)
legend("bottomright", legend=c("Boosted Tree"))

```
Logistic regresson model has the highest overall accuracy against the Validation set, as well as the highest accuracy within segments. It is also has the most optimal ROC. Therefore, I choose to use logistic regression model.
Applying the chosen model, the number of individuals are creditworthy is 413.
```{r predict}
yhat_final <- predict(model1, validation)
print(sum(yhat_final=='Creditworthy'))
```
